Gammapy: A Python package for gamma-ray astronomy

### 2022-12-07 src/ms-review.tex
Modified title

The other sequence, referred to as high-level analysis, deals with the extraction of physical
quantities related to \gammaray sources and the production of high-level products such as spectra,
light curves and catalogs. The methods applied here are more generic and are broadly
shared across the field. They also frequently imply joint analysis of multi-instrument data.
To extract physically relevant information, the measured counts on an instrument are usually
compared to a parametrised model of the true intensity distribution of \gammaray source in a given
field-of-view, which is "forward folded" through a model of the instrument repsonse
to get a prediction for the expected counts measured by the instrument. Parameters
of the model are then estimated using statistical techniques such as maximum likelihood
estimation (MLE).

\subsection{Events and Instrument Response Functions: the Data Level 3}

\gammaray data at the Data Level 3 (DL3) consists in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area,
point spread function (PSF), energy dispersion and residual hadronic background.

@@

@@

@@

After all data has been projected into the same coordinate system, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
the background estimated can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument is typically
associated with a sytematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 "safe" data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).

>>>>

The other sequence, referred to as high-level analysis, deals with the extraction of physical
quantities related to \gammaray sources and the production of high-level products such as spectra,
light curves and catalogs. The methods applied here are more generic and are broadly
shared across the field. They also frequently imply joint analysis of multi-instrument data.
To extract physically relevant information, the measured counts on an instrument are usually
compared to a parametrised model of the true intensity distribution of \gammaray source in a given
field-of-view, which is "forward folded" through a model of the instrument response
to get a prediction for the expected counts measured by the instrument. Parameters
of the model are then estimated using statistical techniques such as maximum likelihood
estimation (MLE).

\subsection{Predicted counts and Instrument Response Functions}

@@

\gammaray data at the Data Level 3 (DL3) therefore consist in lists of gamma-like events and their
corresponding instrument response functions (IRFs). The latter include the effective area,
point spread function (PSF) and energy dispersion.

@@

In practice, the background model is subject to numerous uncertainties and needs to be corrected on the data.
Frequently, a background model is not even available and the background contribution has to be estimated
directly from the data.

@@

After all data has been projected into the same geometry, it is typically
required to improve the residual hadronic background estimate. As residual hadronic
background models can be subject to significant systematic uncertainties,
the background estimated can be improved by taking into account actual data
from regions without known \gammaray sources. This includes methods 
such as the ring or the field-of-view background techniques or
background measurements performed within, e.g. reflected regions~\citep{Berge07}.
Data measured at the field-of-view or energy boundaries of the instrument is typically
associated with a sytematic uncertainty in the IRF. For this reason this part 
of the data is often excluded from subsequent analysis by defining regions of
 "safe" data in the spatial as well as energy dimension.
All of these data reduction steps are performed by classes and functions
implemented in the \code{gammapy.makers} subpackage (see Section~\ref{ssec:gammapy-makers}).
